### 2019-04-15 paper/paper.tex
prepping keyword tables

As we demonstrated in section \ref{metricDiff}, packages that perform well
by one measure of popularity can perform poorly by others. The original paper
proposes that one major source of this differential is in the way that packages
are used \cite{Wittern:2016}. It is surmised that packages ranked highly by the
\code{npm} PageRank system are primarily packages that are used often within the
\code{npm} ecosystem, and tend to be \textbf{core utility} packages that are used
as dependencies for other \code{npm} packages, and rarely used outside of the
\code{npm} package environment. Conversely, packages that exhibit
significant popularity by the \code{GitHub} rank tend to be \textbf{end user} packages more
commonly used in application development as opposed to package construction. 
In order to confirm this hypothesis, we examine keywords associated with each
ranking system, as is done in the original paper.
Tables \ref{npmStrong} and \ref{githubStrong} display keywords most associated with
each popularity ranking. As the keywords in Table \ref{npmStrong} are closely linked to 
low level utilities, and the keywords of Table \ref{githubStrong} are strongly related to
application frameworks, we feel confident confirming the hypothesis of the original authors.

>>>>

As we demonstrated in section \ref{metricDiff}, packages that perform well
by one measure of popularity can perform poorly by others. The original paper
proposes that one major source of this differential is in the way that packages
are used \cite{Wittern:2016}. It is surmised that packages ranked highly by the
\code{npm} PageRank system are primarily packages that are used often within the
\code{npm} ecosystem, and tend to be \textbf{core utility} packages that are used
as dependencies for other \code{npm} packages, and rarely used outside of the
\code{npm} package environment. Conversely, packages that exhibit
significant popularity by the \code{GitHub} rank tend to be \textbf{end user} packages more
commonly used in application development as opposed to package construction. 
In order to confirm this hypothesis, we examine keywords associated with each
ranking system, as is done in the original paper.

\begin{table}
  \centering
  % TODO NOTE THAT THIS HAS LOWER NUMBERS THAN THE ORIGINAL PAPER DUE TO MONTHLY PAGERANKS
  \begin{tabular}{c|c|c|c}
    Keyword & "\code{npm} strong" & "\code{GitHub} strong" & Diff. \\
    \hline
     & - & 0.550 & 0.345\\
     & 0.550 & - & 0.444\\
     & 0.345 & 0.444 & -\\

  \end{tabular}
  \caption{"\code{npm} strong" keywords ordered by difference in occurrence between correlated measures.}
  \label{npmStrong}
\end{table}

\begin{table}
  \centering
  % TODO NOTE THAT THIS HAS LOWER NUMBERS THAN THE ORIGINAL PAPER DUE TO MONTHLY PAGERANKS
  \begin{tabular}{c|c|c|c}
    Keyword  & "\code{GitHub} strong" & "\code{npm} strong" & Diff. \\
    \hline
     & - & 0.550 & 0.345\\
     & 0.550 & - & 0.444\\
     & 0.345 & 0.444 & -\\

  \end{tabular}
  \caption{"\code{GitHub} strong" keywords ordered by difference in occurrence between correlated measures.}
  \label{githubStrong}
\end{table}

Tables \ref{npmStrong} and \ref{githubStrong} display keywords most associated with
each popularity ranking. As the keywords in Table \ref{npmStrong} are closely linked to 
low level utilities, and the keywords of Table \ref{githubStrong} are strongly related to
application frameworks, we feel confident confirming the hypothesis of the original authors.
